\subsection{Hardware}
Our client gave us the task of choosing the equipment we would need in order to build a fully working system that will be implemented at a later stage. Below is a list of equipment we would need for this project and their requirements.

	\subsubsection{Server}
	The system will be deployed on an existing server owned by the University of Pretoria, Department of Computer Science.
	
	\subsubsection{Client}
	The client will be a device installed at the entrance and exit of the buildings where we would want to control access.\\
\\
 The following requirements, listed below, must be met by the client in order to be compatible with the system.
	\begin{itemize}
		\item Capable of running a Linux based operating system.
		\item Can connect to a network.
	\end{itemize}
	
COSBAS will be using a \textbf{Raspberry PI 2 Model B} as the \textbf{client}. This device has a low power consumption, small form factor and is inexpensive. It also meets the requirements listed above. 

	\subsubsection{Camera}
	The camera will be used to capture the facial features of a user, which will be stored temporarily on the client. The client will then send this data to the server for authentication.\\
\\
The camera must satisfy the following requirements:
	\begin{itemize}
		\item Has a minimum horizontal resolution of 1920. %I said 1920 to be safe but once i get the calculations done will update%
		\item Can connect to the Raspberry PI 2 Model B.
		\item Is supported by the operating system on the client.
	\end{itemize}

COSBAS will be using the \textbf{Logitech C525} as the \textbf{ camera} since it met the requirements above.
	
	\subsubsection{Fingerprint Scanner}
	Fingerprint scanners will allow us to capture a user's fingerprint which will then be authenticated on the server against our database. \\
\\
For the fingerprint scanner to be compatible with the system it must meet the following requirements:
	\begin{itemize}
		\item Has a minimum resolution of 500 pixels per inch, which is the standard for a fingerprint scan.
		\item Can connect to the Raspberry PI 2 Model B.
		\item Is supported by the operating system on the client.
	\end{itemize}
	
COSBAS will be using the \textbf{Futronic FS80H} as the \textbf{fingerprint scanner} since it met the requirements above.
	
	\subsubsection{Keypad}
Visitors that do not have biometric access will use the keypad with the temporary access code they received when booking their appointments.

Requirements:
	\begin{itemize}
		\item Can connect to the client.
		\item Is supported by the operating system on the client.
	\end{itemize}


		