\subsubsection{Reliablity}
One of the most important quality requirements for the system is that it should be reliable. The reliability quality requirement is of high importance because the system is based on secure actions.
The system should therefore produce the correct action/output at any given time when the system is in use.\\
\\The system should,
\begin{itemize}
	\item  never \textbf{give access} to someone who should \textbf{not have access}.
	\item  never \textbf{refuse access} to someone that\textbf{ should have access}. 
	\item  \textbf{never lock someone in}. If someone gained authorized access to the building the system should allow him/her to exit the building as well.

\end{itemize}

\subsubsection{Security}
The system needs to be secure, since personal information is stored on the system. Security as a quality requirement means that the system should prevent malicious actions and/or attacks.\\
\\The system should,
\begin{itemize}
	\item  protect the biometric data and other personal information of all users against unauthorized modification/access.
	\item  protect the biometric data against third party applications.
	\item  prevent loss of information (Personal information, Appointments etc.)
\end{itemize}

If security as a requirement is not met then the system can be deemed as unimplementable and worthless, since anyone can just gain access to the building.

\subsubsection{Scalability/Plugability}
The system should be scalable, plugable and generic.\\
\\The scalability includes,
\begin{itemize}
	\item  \textbf{Functional scalability} - Which means to add functionality to the system with minimal effort from developers.
		The system initially will only have facial recognition and fingerprint scanning as the biometric methods, but it should ideally be expanded to be able use any type of biometric method such as voice recognition for example.
	\item  The system needs to \textbf{scale out} (scale horizontally) - Which indicates that the system should be able to add more nodes, that is the system should add more biometric devices, replace existing ones and also add more entry points (entrances/doors), without the loss of performance or any other quality requirement.
\end{itemize}





