\addcontentsline{toc}{section}{References}
\begin{flushleft}

\begin{thebibliography}{99}
	\bibitem[Attard, 2013]{dependency1} Attard, A. (2013) \textit{Why should we use dependency injection?} [Online] Available from: http://www.javacreed.com/why-should-we-use-dependency-injection/ [Accessed 31 July 2015]

	\bibitem [Farcic, 2014]{Farcic2014} Farcic, V. (2014). \textit{Java Build Tools: Ant vs Maven vs Gradle.} [online] Technology. Available at: http://technologyconversations.com/2014/06/18/build-tools/ [Accessed 31 July 2015].

	\bibitem[Fowler, 2004]{dependency2}Fowler, M. (2004) \textit{Inversion of Control Containers and the Dependency Injection pattern}[Online] Available from: http://www.martinfowler.com/articles/injection.html [Accessed 31 July 2015]

	\bibitem [Gradle Documentation, 2015]{GradleDocChap8} Gradle Documentation, (2015). \textit{Chapter 8. Dependency Management Basics.} [online] Available at: https://docs.gradle.org/current/userguide/artifact\_dependencies\_tutorial.html [Accessed 31 July 2015].

	\bibitem [Gradle User Manual, 2015]{GradleChap55} Gradle User Manual, (2015). Chapter 55. Building native binaries. [online] Available at: http://gradle.monochromeroad.com/docs/userguide/nativeBinaries.html [Accessed 31 Jul. 2015].

	\bibitem[Microsoft 2015]{QualityAttrs} Msdn.microsoft.com, (2015). Chapter 16: Quality Attributes. [online]  Available at: https://msdn.microsoft.com/en-us/library/ee658094.aspx [Accessed 29 May 2015].

	\bibitem[MongoDB 2015a]{Mongo} MongoDB. 2015. MongoDB. [ONLINE] Available at: https://www.mongodb.org/. [Accessed 30 July 15].
	
	\bibitem[MongoDB 2015b]{MongoSharding} MongoDB. 2015. Purpose of Sharding. [ONLINE] Available at: http://docs.mongodb.org/manual/core/sharding-introduction [Accessed 30 July 15].

	\bibitem[Spring 2015a]{Spring Introduction} Introduction to the Spring Framework. 2015. Introduction to the Spring Framework. [ONLINE] Available at: http://www.theserverside.com/news/1364527/Introduction-to-the-Spring-Framework. [Accessed 31 July 2015].
	
	\bibitem[Spring 2015b]{Spring Advantages} Five Advantages of Spring Framework | Orange Slate. 2015. Five Advantages of Spring Framework | Orange Slate. [ONLINE] Available at: http://orangeslate.com/2006/11/10/five-advantages-of-spring-framework/. [Accessed 31 July 2015].
	
	\bibitem[Spring 2015c]{Spring Interview Questions} Spring Interview Questions FAQs Interview Questions Spring Tutorial JSF Interview Questions Hibernate Interview Questions. 2015. Spring Interview Questions FAQs Interview Questions Spring Tutorial JSF Interview Questions Hibernate Interview Questions. [ONLINE] Available at: http://www.developersbook.com/spring/interview-questions/spring-interview-questions-faqs.php. [Accessed 31 July 2015].
	
	\bibitem[Spring 2015d]{Spring vs JavaEE i.} Why using Spring instead of JEE6? - Spring Forum . 2015. Why using Spring instead of JEE6? - Spring Forum . [ONLINE] Available at: http://forum.spring.io/forum/spring-projects/container/124744-why-using-spring-instead-of-jee6. [Accessed 31 July 2015].
	
	\bibitem[Spring 2015e]{Spring vs JavaEE ii.} Spring advantages over current Java EE - Stack Overflow. 2015. Spring advantages over current Java EE - Stack Overflow. [ONLINE] Available at: http://stackoverflow.com/questions/16234864/spring-advantages-over-current-java-ee. [Accessed 31 July 2015].
	
	\bibitem[Spring 2015f]{Spring Benefits} What are the benefits of using spring framework.What is Inversion of control ( IOC ), Aspect Oriented Programming(AOP)|SimpleCodeStuffs. 2015. What are the benefits of using spring framework.What is Inversion of control ( IOC ), Aspect Oriented Programming(AOP)|SimpleCodeStuffs. [ONLINE] Available at: http://www.simplecodestuffs.com/basic-concepts-of-spring/. [Accessed 31 July 2015].
	
	\bibitem[Spring 2015g]{Spring} Spring. 2015. Spring Data MongoDB. [ONLINE] Available at: http://projects.spring.io/spring-data-mongodb/. [Accessed 30 July 15].

	\bibitem [Timošin, 2013]{Timosin2013} Timošin, J. (2013). \textit{Java Build Tools: Maven, Gradle and Ant plus the DSL vs. XML debate.} [online] Zeroturnaround.com. Available at: http://zeroturnaround.com/rebellabs/java-build-tools-maven-gradle-and-ant-plus-the-dsl-vs-xml-debate/~[Accessed~31~July~2015].

\end{thebibliography}
\end{flushleft}
