\bibitem[Spring 2015a]{Spring Introduction} Introduction to the Spring Framework. 2015. Introduction to the Spring Framework. [ONLINE] Available at: http://www.theserverside.com/news/1364527/Introduction-to-the-Spring-Framework. [Accessed 31 July 2015].
	
\bibitem[Spring 2015b]{Spring Advantages} Five Advantages of Spring Framework | Orange Slate. 2015. Five Advantages of Spring Framework | Orange Slate. [ONLINE] Available at: http://orangeslate.com/2006/11/10/five-advantages-of-spring-framework/. [Accessed 31 July 2015].
	
\bibitem[Spring 2015c]{Spring Interview Questions} Spring Interview Questions FAQs Interview Questions Spring Tutorial JSF Interview Questions Hibernate Interview Questions. 2015. Spring Interview Questions FAQs Interview Questions Spring Tutorial JSF Interview Questions Hibernate Interview Questions. [ONLINE] Available at: http://www.developersbook.com/spring/interview-questions/spring-interview-questions-faqs.php. [Accessed 31 July 2015].
	
\bibitem[Spring 2015d]{Spring vs JavaEE i.} Why using Spring instead of JEE6? - Spring Forum . 2015. Why using Spring instead of JEE6? - Spring Forum . [ONLINE] Available at: http://forum.spring.io/forum/spring-projects/container/124744-why-using-spring-instead-of-jee6. [Accessed 31 July 2015].
	
\bibitem[Spring 2015e]{Spring vs JavaEE ii.} Spring advantages over current Java EE - Stack Overflow. 2015. Spring advantages over current Java EE - Stack Overflow. [ONLINE] Available at: http://stackoverflow.com/questions/16234864/spring-advantages-over-current-java-ee. [Accessed 31 July 2015].
	
\bibitem[Spring 2015f]{Spring Benefits} What are the benefits of using spring framework.What is Inversion of control ( IOC ), Aspect Oriented Programming(AOP)|SimpleCodeStuffs. 2015. What are the benefits of using spring framework.What is Inversion of control ( IOC ), Aspect Oriented Programming(AOP)|SimpleCodeStuffs. [ONLINE] Available at: http://www.simplecodestuffs.com/basic-concepts-of-spring/. [Accessed 31 July 2015].
	